Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-25 paper-v1.tex
fix AntsReview implementation

\subsubsection{AntsReview}
AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
\newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to specify the amount of Ether for the reward, to be stored in the contract balance.
\end{itemize}

\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.

>>>>

\subsubsection{AntsReview}
AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
\newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to specify the amount of Ether for the reward, to be stored in the contract balance.
\end{itemize}

\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
